Poseidon Adventure

### 2019-06-05 SardinesOnlyatlantisom2SStest.Rmd
fix census, scale catch bio

# apply default sample fish to get numbers, effNhigh samples all, see census_spec
numssshigh <- sample_fish(survey_N_ss, effNhigh)

@@

# get catch lengths and wtage
catch_length_census_ss <- calc_age2length(structn = catch_structnss,
                                 resn = catch_resnss,
                                 nums = catch_numssshigh,
                                 biolprm = truth$biolprm, fgs = truth$fgs,
                                 maxbin = 150,
                                 CVlenage = 0.1, remove.zeroes=TRUE)

@@

totcatchann <- totcatchN %>%
  mutate(yr = floor(time/fstepperyr)) %>%
  group_by(species, yr) %>%
  summarise(anncatchage = sum(atoutput))
# 
# totcatch <- totcatchage %>%   
#   group_by(species, yr) %>%
#   summarise(truecatch = sum(anncatchage))
# 
plottotC <- ggplot(totcatchann, aes(x=yr, y=anncatchage)) +
  geom_point() +
  theme_tufte() +
  labs(subtitle = paste(scenario.name,
                        catchage$species))

@@

@@

Do some comparisons of biomass surveys with truth. Something is going way wrong in the calculation of survey biomass based on numbers times weight at age, looks like division by 1000 could fix it? Actually no the true biomass based on survey is wrong.

@@

if (fstepperyr>1){
  #need to take all output time steps and sum catch over each year
  catch_numbers_area <- catch_numbers %>%
    #assign a temporary year column, aggregate nums over this year
    mutate(yr = floor(time/fstepperyr)) %>%
    group_by(species, agecl, polygon, yr) %>%
    summarise(anncatch_area=sum(atoutput))

@@

@@

@@

@@

```{r SS-write-ts}

>>>>

# apply default sample fish to get numbers, effNhigh samples all, see census_spec
# NOPE! effNhigh is not big enough for census of sardines, bigger breaks function
#numssshigh <- sample_fish(survey_N_ss, effNhigh)

numsss <- aggregate(survey_N_ss$atoutput,list(survey_N_ss$species,survey_N_ss$agecl,survey_N_ss$time),sum)
names(numsss) <- c("species","agecl","time","atoutput")
numssshigh <- data.frame(species = numsss$species,
					  agecl = numsss$agecl,
					  polygon = NA,
					  layer = NA,
					  time = numsss$time,
					  atoutput = numsss$atoutput)

@@

# get catch lengths and wtage at every timestep
catch_length_census_ss <- calc_age2length(structn = catch_structnss,
                                 resn = catch_resnss,
                                 nums = catch_numssshigh,
                                 biolprm = truth$biolprm, fgs = truth$fgs,
                                 maxbin = 150,
                                 CVlenage = 0.1, remove.zeroes=TRUE)

@@

@@

Do true catch numbers times weight at age match catch in biomass? No. It is about 16 times too high relative to catch.txt output, and shifted one year back (which is due to the floor function, and an easy fix).

```{r catchNtoB}

totcatchann <- totcatchN %>%
  mutate(yr = floor(time/fstepperyr)+1) %>%
  group_by(species, yr) %>%
  summarise(anncatchage = sum(atoutput))

plottotC <- ggplot(totcatchann, aes(x=yr, y=anncatchage)) +
  geom_point() +
  theme_tufte() +
  labs(subtitle = paste("Catch in N ", scenario.name,
                        totcatchann$species))

catch_lengthwt_census_ss <- readRDS(file.path(d.name, paste0(scenario.name, "catchlengthwt_census_sard.rds")))

CwtAtAge <- catch_lengthwt_census_ss$muweight %>%
  select(species, agecl, time, wtAtAge = atoutput) %>%
  mutate(wtAtAge = wtAtAge/1000)

catchbioN_ss <- merge(catch_numssshigh,CwtAtAge,by=c("species","agecl", "time"),all.x=T) %>%
  mutate(biomass = atoutput*wtAtAge/1000) %>%
  mutate(yr = floor(time/fstepperyr)+1) %>%
  group_by(species, yr) %>%
  summarise(anncatchB = sum(biomass))

plotcatch <- ggplot() +
  geom_line(data=truecatchbio_ss, aes(x=time/365,y=atoutput, color="true catch bio from txt"),
            alpha = 10/10) +
  geom_point(data=catchbioN_ss, aes(x=yr,y=anncatchB/16, color="true catch bio from N/16"),
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

@@

Do some comparisons of biomass surveys with truth.

@@

if (fstepperyr>1){
  #need to take all output time steps and sum catch over each year
  catch_numbers_area <- catch_numbers %>%
    #assign a temporary year column, aggregate nums over this year
    mutate(yr = floor(time/fstepperyr)+1) %>%
    group_by(species, agecl, polygon, yr) %>%
    summarise(anncatch_area=sum(atoutput))

@@

Check this against true total catch numbers above. Should be the same.

```{r compare-totcatch}

compareC <- ggplot() +
  geom_line(data=totcatchann, aes(x=yr, y=anncatchage, color="census catch N"), 
            alpha = 10/10) +
  geom_point(data=catch_total, aes(x=yr,y=catch, color="sample catch N"), 
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

compareC +
  facet_wrap(~species, scales="free")

@@

#Sample fish for age composition from survey
age_comp_data <- sample_fish(survey_out, highEffN)

@@

Can we match catch in weight from catch.txt? No, see above.

```{r compareC-wt, eval=FALSE}

plotcatch <- ggplot() +
  geom_line(data=truecatchbio_ss, aes(x=time/365,y=atoutput, color="true catch bio"),
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

@@

```{r SS-write-ts, eval=FALSE}

### 2019-06-05 docs/index.Rmd
fix census, scale catch bio

<a href="https://sgaichas.github.io/poseidon-dev/SardinesOnlyatlantisom2SStest.html" target="_blank">Start on Sardines in the CalCurrent, all true and SS data, May 31, 2019, updated June 3</a>

>>>>

<a href="https://sgaichas.github.io/poseidon-dev/SardinesOnlyatlantisom2SStest.html" target="_blank">Start on Sardines in the CalCurrent, all true and SS data, May 31, 2019, updated June 5</a>
